---
# Some notes:
# Please see https://github.com/HanZhang-psych/CV
# - basic information is in the first section and can be updated easily
# - there are several csv files in the current directory which can be edited / added to, which should update automatically when knitted. E.g., you have to add your presentations to the .csv

## .bib files!
# - publications are within the "Published.bib" file. This .bib file is exported from orcid. So you may need to update orcid (though it does some things automatically)
# - preprints are within "Preprints.bib". This .bib file is scraped from google scholar.
# - datasets and theses were just created manually (given that these rarely update)
# - all the .bib files are read in as text and then my name is bolded. For the datasets and theses this was done manually

address: Center for Molecular and Behavioral Neuroscience, Rutgers University
date: "`r format(Sys.time(), '%B %Y')`"
email: lukehearne@gmail.com
github: ljhearne
name: Luke
output: 
  vitae::awesomecv:
    pandoc_args: ["--lua-filter=multiple-bibliographies.lua"] # used for creating bibliographies for multiple sections
csl: apa-cv.csl # change this if you want to use other citation styles
phone: +61 4 2492 2254
position: Postdoctoral researcher
surname: Hearne
headcolor: 414141
twitter: LukeJHearne
www: luke-hearne.netlify.app
bibliography_published: "Published.bib"
bibliography_preprints: "Preprints.bib" 
bibliography_theses: "Theses.bib" 
bibliography_data: "Datasets.bib" 
nocite: '@*' # don't change this if you want to print out all the refs
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae);library(tibble);library(dplyr)
```
# Overview
I am an early career researcher interested in the large-scale functional and structural organization of the brain, and how it relates to cognition and mental health. I use a combination of neuroimaging, computational modeling and network science to investigate these questions.

# Current positions
```{r current employment}
emp <- do.call("bind_rows",rorcid::orcid_employments("0000-0002-2014-1148")$`0000-0002-2014-1148`$`affiliation-group`$summaries)

# find NA entries in the year and change to current, and index the entire dataframe
idx = is.na(emp$`employment-summary.end-date.year.value`)
emp$`employment-summary.end-date.year.value`[idx] = "Current"
emp = emp[idx,]

emp %>%
  detailed_entries(
    what = `employment-summary.role-title`,
    when = glue::glue("{`employment-summary.start-date.year.value`} - {`employment-summary.end-date.year.value`}"),
    with = glue::glue("{`employment-summary.organization.name`}: {`employment-summary.department-name`}"),
    where = glue::glue("{`employment-summary.organization.address.city`} - {`employment-summary.organization.address.country`}")
  )
```

# Previous positions
```{r previous employment}
emp <- do.call("bind_rows",rorcid::orcid_employments("0000-0002-2014-1148")$`0000-0002-2014-1148`$`affiliation-group`$summaries)

# find NA entries in the year and change to current, and index the entire dataframe
idx = is.na(emp$`employment-summary.end-date.year.value`)
emp = emp[!idx,]

emp %>%
  detailed_entries(
    what = `employment-summary.role-title`,
    when = glue::glue("{`employment-summary.start-date.year.value`} - {`employment-summary.end-date.year.value`}"),
    with = glue::glue("{`employment-summary.organization.name`}: {`employment-summary.department-name`}"),
    where = glue::glue("{`employment-summary.organization.address.city`} - {`employment-summary.organization.address.country`}")
  )
```
# Education
```{r education}

edu <- do.call("bind_rows",
  rorcid::orcid_educations("0000-0002-2014-1148")$`0000-0002-2014-1148`$`affiliation-group`$summaries
)
edu %>%
  detailed_entries(
    what = `education-summary.role-title`,
    when = glue::glue("{`education-summary.start-date.year.value`} - {`education-summary.end-date.year.value`}"),
    with = glue::glue("{`education-summary.organization.name`}: {`education-summary.department-name`}"),
    where = `education-summary.organization.address.city`
  )
```
# Publications
## Peer reviewed
```{r peer reviewed pubs}
orcid_id <- c("0000-0002-2014-1148")
my_dois <- rorcid::identifiers(rorcid::works(orcid_id))
pubs <- rcrossref::cr_cn(dois = my_dois, format = "bibtex")
invisible(lapply(pubs, write, "Published.bib", append=TRUE))

raw_text  <- readLines("Published.bib")
new_text  <- gsub("Luke Hearne", "{\\\\bf Hearne, L. J}", raw_text)
writeLines(new_text, con="Published.bib")

raw_text  <- readLines("Published.bib")
new_text  <- gsub("Luke J. Hearne", "{\\\\bf Hearne, L. J}", raw_text)
writeLines(new_text, con="Published.bib")
```
<!-- Notes: copy and paste the following block for any other bibliography sections with the same bibliography key matched that you assigned in YAML  -->
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_published}
:::

\endgroup
<!-- Bib-printing block ends here. -->

## Preprints
```{r preprint pubs}
df = scholar::get_publications("sd1s1kAAAAAJ&")
if (sum(df$journal=="bioRxiv") > 0 || sum(df$journal=="BioRxiv") > 0) {
  do_preprints=1
} else {
  do_preprints=0
}

if (do_preprints==1) {
  scholar::get_publications("sd1s1kAAAAAJ&") %>%
    arrange(desc(year)) %>%
    filter(grepl('bioRxiv|BioRxiv', journal)) %>%
    distinct(title, .keep_all = TRUE) %>%
    transmute(bibtype = "Article", author = as.character(author),
              title = as.character(title),
              journaltitle = as.character(journal), year, key = row_number()) %>% 
    RefManageR::as.BibEntry() %>% 
    RefManageR::WriteBib("Preprints.bib")
} else {file.create("Preprints.bib")}

raw_text  <- readLines("Preprints.bib")
new_text  <- gsub("LJ Hearne", "{\\\\bf Hearne, L. J}", raw_text)
writeLines(new_text, con="Preprints.bib")
```
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_preprints}
:::

\endgroup

## Theses

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_theses}
:::

\endgroup
## Data
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_data}
:::

\endgroup

# Funding and awards

## Funding
```{r}
library(tibble)
read.csv('funding_and_awards.csv') %>%
  arrange(desc(Year)) %>%
  filter(grepl('Funding', Type)) %>%
  brief_entries(what=Award,when=Year,with=Desc)
```

## Awards
```{r}
read.csv('funding_and_awards.csv') %>%
  arrange(desc(Year)) %>%
  filter(grepl('Award', Type)) %>%
  brief_entries(what=Award,when=Year,with=Desc)
```
# Presentations
## Invited talks
```{r}

read.csv('presentations.csv') %>%
  arrange(desc(Year)) %>%
  filter(grepl('Invited', Type)) %>%
  brief_entries(what=glue::glue("{Title}. {Where}"),
                when=Year)
```
## Conference talks
```{r}

read.csv('presentations.csv') %>%
  arrange(desc(Year)) %>%
  filter(grepl('Talk', Type)) %>%
  brief_entries(what=glue::glue("{Title}. {Where}"),
                when=Year)
```
## Conference posters
```{r}

read.csv('presentations.csv') %>%
  filter(grepl('Poster', Type)) %>%
  brief_entries(what=glue::glue("{Title}. {Where}"),
                when=Year)
```

# Teaching, service and public outreach

## Supervision
```{r}
read.csv('teaching_supervision.csv') %>%
brief_entries(what=Description, with=Role,when=Year)
```
## Service
```{r}
read.csv('service.csv') %>%
brief_entries(what=Description, with=Role,when=Year)
```

## Media coverage
```{r}
read.csv('media.csv') %>%
  arrange(desc(Year)) %>%
  brief_entries(what=TitleLink, when=Year,
                .protect = FALSE)

```